Automated Synthesis of State-Space Digital Systems

### 2017-01-16 cav2017/cav2017.tex
some revising

% first the title is needed
\title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants}

@@

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability, working typically on continuous domains
\cite{sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.  Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.
In this paper, however, we propose the synthesis of control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant, alongside the discrete domain of the controller and the
hybrid elements that communicate them.

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of Counter-Example Guided Abstraction Refinement (CEGAR),
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

@@

%-------------------------------
\subsection{Related Work}
\label{sec:relw}
%-------------------------------

\todo{[Move material from \ref{sec:rw} here]}

@@

%-------------------------------
\subsection{State-space representation of physical systems} 
\label{ssec:ssrepresentation}
%-------------------------------

We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
\end{align}
where $A$ and $B$ are matrices that fully specify the continuous plant.  
\todo{[specify initial conditions? specify input ranges already here? ]} 
Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align}
%
The

%-------------------------------
\subsection{Controller synthesis via state feedback}
\label{ssec:statefeedbackcontrol}
%-------------------------------

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback can be employed to affect the properties and behaviours of the process. 
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
The most basec feedback architecture is the state feedback, 
where the control action $\vec{u}_k$ is computed by: 
%
\begin{equation}
u_k = r_{k} - K x_k, 
\end{equation}
%
where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal.   
%
The closed-loop model then takes the form 
\begin{align}
x_{k+1} = ( A_d - B_d K ) + B_d r_k. \nonumber
\end{align}
The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
according to a desired goal or objective. 
A standard objective is to obtain stable closed-loop dynamics.

\todo{[Here discuss Jury criterium]}

\bigskip

\todo{[Unclear what the remainder of the section serves for. ]}
The output and measurable of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}
\commentib{What is S?}

@@

%-------------------------------
\subsection{Digital implementation of feedback controller}
\label{ssec:statefeedbackcontrol}
%-------------------------------

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Controllers for LTI Systems} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%-------------------------------
\section{Related Work}
\label{sec:rw}
%-------------------------------

@@

%-------------------------------
\section{Extensions}
\label{sec:extensions}
%-------------------------------

%-------------------------------
\subsection{LTI systems with output} 
\label{ssec:LTI}
%-------------------------------

LTI models in the form: 
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
\end{align}
%

>>>>

% first the title is needed
\title{Automated Synthesis of State-Space Digital Systems}

@@

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability %, working typically on continuous domains
\cite{sadabadi2016static, DBLP:journals/corr/AbateBCCDKK16}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.

Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.
In this paper, however, we propose the synthesis of control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant, alongside the discrete domain of the controller and the
hybrid elements that communicate them.

In this paper, we synthesize controllers for hybrid
closed-loop systems, i.e., software-implemented embedded controllers along
with a model of their physical environment (the plant), that are
\emph{safe}.  Due to the complexity of such systems, in this work we focus
on linear models with known configurations and perform parametric synthesis
of safe digital controllers.
To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of abstraction refinement
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

@@

@@

%-------------------------------
\subsection{State-space representation of dynamical systems}
\label{ssec:ssrepresentation}
%-------------------------------

In this study, we focus on Cyber-Physical Systems with continuous 
dynamical plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
\end{align}
\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
(as shown in the appendix) into
%
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
\end{align}
%

%-------------------------------
\subsection{State feedback control}
\label{ssec:statefeedbackcontrol}
%-------------------------------

Feedback control is usually employed to modify and control the properties and behaviors of process and systems, reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. A well-known feedback control technique is the state feedback control where the control action $\vec{u}_k$ is computed by:
%
\begin{equation}
\vec{u}_k=\vec{r}_{k}-\mat{K}\vec{x}_k.
\end{equation}
%
where $\mat{K} \in \mathbb{R}^{m \times o}$ is the state feedback gain matrix.
%
The output and measurable of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\end{align*}
\commentib{What is S?}

@@

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Counterexample Guided Abstractly Refined Inductive Synthesis for LTI Cyberphysical Systems}\label{sec:CEGARIS}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

{\bf Assumption:} We consider the reference signal to be 0, whereas the initial states are non-deterministic.

\todo{Explain the implicaitions of this.}

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Verification of a Conrollable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%-------------------------------
\section{Related Work}
%-------------------------------

@@
